Minimum Uncertainty JPDA Filters and Coalescence Avoidance for Multiple Object Tracking \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2018-06-09 Journal/JAS Data Association/JAS_DataAssoc.tex
journal added

In short, the main contributions of this paper are (i) deriving the optimal JPDAF that minimizes the posterior mean square error and uncertainties in estimation, and (ii) proposing a systematic approach to avoid data coalescence of multiple objects in close-proximity. The desirable features of the proposed approaches are illustrated by extensive numerical simulations with satellites in orbits.

@@

The proposed coalescence avoiding filtering algorithm is constructed by minimizing the cost function $\mathbf{J}\in\Re$, defined as as the sum of the uncertainty cost $J_P\in\Re$ and similarity cost $J_S\in\Re$ with positive weighting factor $c\in\Re$,
\begin{align}
\label{eqn:CostGen}
\mathbf{J}=J_P+cJ_S.
\end{align}
%The estimator gain $K_i$ is selected to minimize the above cost $\mathbf{J}$. In short, the estimator gain is chosen in the consideration of both uncertainty and coalescence, illustrated in Figure \ref{fig:CostTrends}.
The estimator gain $K_i$ is selected to minimize the above cost $\mathbf{J}$. By considering similarity to obtain the estimator gain, we mitigate some coalescence at the expense of increasing estimate uncertainty according to the magnitude of $c$.
The choice of $c$ depends on the type of scenario and the parameter $a$ shapes the similarity cost $J_S$.

\begin{figure}
\setlength{\unitlength}{0.06\columnwidth}
\centerline{\footnotesize\selectfont
\begin{picture}(8.5,7.3)(-0.5,-0.8)
\put(-0.5,3){\rotatebox{90}{Cost}}
\put(0,0){\includegraphics[width=0.48\columnwidth]{CT.png}}
\put(5.3,1.2){\shortstack[c]{Uncertainty\\ cost: $J_P$}}
\put(6.2,2.6){\shortstack[c]{Similarity\\ cost: $J_S$}}
\put(5.2,5.2){\shortstack[c]{Weighted sum:\\ $\mathbf{J}=J_P+cJ_S$}}
%\put(4.98,0.78){\circle*{0.1}}
%\put(2.48,1.57){\circle*{0.1}}
%\put(5.00,0.81){\circle*{0.1}}
%\put(2.47,1.60){\circle*{0.1}}
\put(4.99,0.81){\circle*{0.1}}
\put(2.47,1.60){\circle*{0.1}}
\put(4.8,-0.4){$K_\text{M-JPDAF}$}
\put(2.3,-0.4){$K_\text{C-JPDAF}$}
\put(3.1,-0.8){Estimator gain}
\end{picture}
}
\caption{Illustration of optimal coalescence avoidance: several costs are illustrated with respect to an element of an estimator gain $K$ (blue dashed: uncertainty cost $J_P$, red dashed-dotted: similarity cost $J_S$, black solid: weighted sum). The estimator gain $K_\text{M-JPDAF}$ is selected to minimize the uncertainty cost. The estimator gain $K_\text{C-JPDAF}$ is chosen such that the weighted sum of the uncertainty cost and the similarity cost is minimized. In short, at the expense of increased uncertainty at a single step, the proposed approach prevents coalescence. The increased uncertainty at each step is rewarded by reducing the overall estimation error drastically by maintaining correct data association during close proximity tracking scenarios or missions.}
\label{fig:CostTrends}
\end{figure}

@@

Necessary conditions for optimality are given by
\begin{align}
\deriv{\mathbf{J}}{K_i} = \deriv{J_P}{K_i} + c \deriv{J_S}{K_i} =0,\label{eqn:NCO}
\end{align}
where $\deriv{J_P}{K_i}$ and $\deriv{J_S}{K_i}$ may be nonzero, so the result may be different than \refeqn{GainK}, which only considers state estimate uncertainty in the optimization.
In short, \refeqn{CostP} and \refeqn{JSK} are substituted into \refeqn{NCO} and repeated for all $p$ to obtain $n_t$ optimal gain matrices.
Then, the C-JPDAF is completed by updating the state estimate and covariance by using \refeqn{KalEst} and \refeqn{JPDAFCov}, respectively.

@@

%For each following scenario, several cases are simulated where various parameters are slightly changed with $\epsilon\in\Re$, summarized in Table \ref{tab:CaseDef}, and measurement are simulated with \refeqn{NonLin2BP} and \refeqn{zj}.
In the following scenarios, several cases are simulated with \refeqn{NonLin2BP} and measurements are generated according to \refeqn{zj}, but the measurement origins are not given to the data association algorithm.
Additionally, there is a $10\%$ chance that a measurement is either deleted or an extraneous measurement is added at each time step.
Since this probability is relatively small, the association probabilities are computed with \refeqn{betaDef} using $B=0$.
Further descriptions of the cases are available below, and the resulting accuracy over $n$ time steps is measured with RMS position (kilometers) and angular (radian) errors, defined as
\begin{align}
% MATLAB: RMS_r_indiv(k) = (sum((Ri{k}-Rhati{k}).^2)/NumStates).^0.5;
\mathbf{e}_{RMS,r,i}=\sqrt{\frac{\sum_{k=1}^n\norm{r_{i,k}-\hat r_{i,k}}^2}{n}}
, \quad
\mathbf{e}_{RMS,\theta,i}=\sqrt{\frac{\sum_{k=1}^n(\cos^{-1}(r_{i,k}^T\hat r_{i,k}))^2}{n}}
,
\end{align}
respectively, and the subsequent tabulated RMS errors are averaged over all objects. 
The position RMS error metrics are decomposed into range and direction components because range measurements are available in LEO cases and angles-only measurements are available in GEO cases.
The uncertainty is summarized with $\tr{J_P}$, and the computation time is measured as well, tabulated in Tables \ref{tab:I}--\ref{tab:IV}.
Scenarios I and II are data association and filtering examples in LEO, while scenarios III and IV are GEO examples.
For readers with interest in how the algorithms handle perturbations, various parameters are slightly changed, tabulated at each scenario description.
The metrics from the perturbed cases are summarized in the subsequent tables as well.

>>>>

%In short, the main contributions of this paper are (i) deriving the optimal JPDAF that minimizes the posterior mean square error and uncertainties in estimation, and (ii) proposing a systematic approach to avoid data coalescence of multiple objects in close-proximity. The desirable features of the proposed approaches are illustrated by extensive numerical simulations with satellites in orbits.
In short, the main contributions of this paper are (i) deriving the optimal JPDAF that minimizes the trace of the posterior state covariance matrix, and (ii) proposing a systematic approach to avoid data coalescence of multiple objects in close-proximity. The desirable features of the proposed approaches are illustrated by extensive numerical simulations with satellites in orbits.

@@

The proposed coalescence avoiding filtering algorithm is constructed by minimizing the cost function $\mathcal{J}\in\Re$, defined as as the sum of the uncertainty cost $J_P\in\Re$ and similarity cost $J_S\in\Re$ with positive weighting factor $c\in\Re$,
\begin{align}
\label{eqn:CostGen}
\mathcal{J}=J_P+cJ_S.
\end{align}
%The estimator gain $K_i$ is selected to minimize the above cost $\mathbf{J}$. In short, the estimator gain is chosen in the consideration of both uncertainty and coalescence, illustrated in Figure \ref{fig:CostTrends}.
The estimator gain $K_i$ is selected to minimize the above cost $\mathcal{J}$. By considering similarity to obtain the estimator gain, we mitigate some coalescence at the expense of increasing estimate uncertainty according to the magnitude of $c$.
The choice of $c$ depends on the type of scenario and the parameter $a$ shapes the similarity cost $J_S$.

\begin{figure}
\setlength{\unitlength}{0.06\columnwidth}
\centerline{\footnotesize\selectfont
\begin{picture}(8.5,7.3)(-0.5,-0.8)
\put(-0.5,3){\rotatebox{90}{Cost}}
\put(0,0){\includegraphics[width=0.48\columnwidth]{CT.png}}
\put(5.3,1.2){\shortstack[c]{Uncertainty\\ cost: $J_P$}}
\put(6.2,2.6){\shortstack[c]{Similarity\\ cost: $J_S$}}
\put(5.2,5.2){\shortstack[c]{Weighted sum:\\ $\mathcal{J}=J_P+cJ_S$}}
%\put(4.98,0.78){\circle*{0.1}}
%\put(2.48,1.57){\circle*{0.1}}
%\put(5.00,0.81){\circle*{0.1}}
%\put(2.47,1.60){\circle*{0.1}}
\put(4.99,0.81){\circle*{0.1}}
\put(2.47,1.60){\circle*{0.1}}
\put(4.8,-0.4){$K_\text{M-JPDAF}$}
\put(2.3,-0.4){$K_\text{C-JPDAF}$}
\put(3.1,-0.8){Estimator gain}
\end{picture}
}
\caption{Illustration of optimal coalescence avoidance: several costs are illustrated with respect to an element of an estimator gain $K$ (blue dashed: uncertainty cost $J_P$, red dashed-dotted: similarity cost $J_S$, black solid: weighted sum). The estimator gain $K_\text{M-JPDAF}$ is selected to minimize the uncertainty cost. The estimator gain $K_\text{C-JPDAF}$ is chosen such that the weighted sum of the uncertainty cost and the similarity cost is minimized. In short, at the expense of increased uncertainty at a single step, the proposed approach prevents coalescence. The increased uncertainty at each step is rewarded by reducing the overall estimation error drastically by maintaining correct data association during close proximity tracking scenarios or missions.}
\label{fig:CostTrends}
\end{figure}

@@

Necessary conditions for optimality are given by
\begin{align}
\deriv{\mathcal{J}}{K_i} = \deriv{J_P}{K_i} + c \deriv{J_S}{K_i} =0,\label{eqn:NCO}
\end{align}
where $\deriv{J_P}{K_i}$ and $\deriv{J_S}{K_i}$ may be nonzero, so the result may be different than \refeqn{GainK}, which only considers state estimate uncertainty in the optimization.
In short, \refeqn{CostP} and \refeqn{JSK} are substituted into \refeqn{NCO} and repeated for all $p$ to obtain $n_t$ optimal gain matrices.
Then, the C-JPDAF is completed by updating the state estimate and covariance by using \refeqn{KalEst} and \refeqn{JPDAFCov}, respectively.

@@

%For each following scenario, several cases are simulated where various parameters are slightly changed with $\epsilon\in\Re$, summarized in Table \ref{tab:CaseDef}, and measurement are simulated with \refeqn{NonLin2BP} and \refeqn{zj}.
In the following scenarios, several cases are simulated with \refeqn{NonLin2BP} and measurements are generated according to \refeqn{zj}, but the measurement origins are not given to the data association algorithm.
Additionally, there is a $10\%$ chance that a measurement is either deleted or an extraneous measurement is added at each time step.
Since this probability is relatively small, the association probabilities are computed with \refeqn{betaDef} using $B=0$.
Further descriptions of the cases are available below, and the resulting accuracy over $n$ time steps is measured with RMS position (kilometers) and angular (radian) errors, defined as
\begin{align}
% MATLAB: RMS_r_indiv(k) = (sum((Ri{k}-Rhati{k}).^2)/NumStates).^0.5;
{e}_{RMS,r,i}=\sqrt{\frac{\sum_{k=1}^n\norm{\mathbf{r}_{i,k}-\hat{\mathbf{r}}_{i,k}}^2}{n}}
, \quad
{e}_{RMS,\theta,i}=\sqrt{\frac{\sum_{k=1}^n(\cos^{-1}(\mathbf{r}_{i,k}^T\hat{\mathbf{r}}_{i,k}))^2}{n}}
,
\end{align}
respectively, and the subsequent tabulated RMS errors are averaged over all objects. 
The position RMS error metrics are decomposed into range and direction components because range measurements are available in LEO cases and angles-only measurements are available in GEO cases.
The uncertainty is summarized with $\tr{J_P}$, and the computation time is measured as well, tabulated in Tables \ref{tab:I}--\ref{tab:IV}.
Scenarios I and II are data association and filtering examples in LEO, while scenarios III and IV are GEO examples.
For readers with interest in how the algorithms handle perturbations, various parameters are slightly changed, tabulated at each scenario description.
The metrics from the perturbed cases are summarized in the subsequent tables as well.
